---
title: "Sample 3"
author: "Jose Zavala"
output: html_document
---

```{r load-libraries include=FALSE}
library(tidyverse)
library(readxl) 
library(IncomPair)
library(exactRankTests)
library(reshape) #melt function, need it for ggplot side by side bar plots
library(ggpubr) #create publishable tables, might not need
```


```{r read-data}
dataNames = read_excel("filepath.xlsx",
                       sheet = 1, skip = 0, n_max = 0) %>% names()

data = read_excel("filepath.xlsx",
                    sheet = 1, skip = 2, col_names = dataNames)

df = data

#names(df)
#view(df)
```

### Data Cleaning and Preprocessing
```{r as-numeric}
# Age - numeric response
df$Q11_1_TEXT = as.numeric(df$Q11_1_TEXT)


df$Q12_1_TEXT= as.numeric(df$Q12_1_TEXT)
```

### Demographics

```{r demographics}
mean(df$Q11_1_TEXT, na.rm = TRUE)
by_gender = df %>% group_by(Q10)  %>% dplyr::summarize(count = n(), AvgAge = mean(Q11_1_TEXT, na.rm = TRUE))
by_gender 


by_capacity = df %>% group_by(Q9) %>% summarise(count = n())
by_capacity

by_setting = df %>% group_by(Q14) %>% summarise(count = n())
by_setting

mean(df$Q12_1_TEXT, na.rm = T)
median(df$Q12_1_TEXT, na.rm = T)

median(df$Q11_1_TEXT, na.rm = TRUE)
mean(df$Q11_1_TEXT, na.rm = TRUE)

```

### Knowledge Questions Pre and Post

```{r knowledge-counts}
# Knowledge Questions 

#1. Knowledge Q1

left_join(count(df, level = as.factor(Q15), name = "pre"), count(df, level = as.factor(Q15B), name = "post")) |> mutate(across(pre:post, ~replace_na(., 0)))

#2. Knowledge Q2

left_join(count(df, level = as.factor(Q16), name = "pre"), count(df, level = as.factor(Q16B), name = "post")) |> mutate(across(pre:post, ~replace_na(., 0)))

#3. Knowledge Q3

left_join(count(df, level = as.factor(Q17), name = "pre"), count(df, level = as.factor(Q17B), name = "post")) |> mutate(across(pre:post, ~replace_na(., 0)))

#4. Knowledge Q4

left_join(count(df, level = as.factor(Q18), name = "pre"), count(df, level = as.factor(Q18B), name = "post")) |> mutate(across(pre:post, ~replace_na(., 0)))

# 5. Knowledge Q5

left_join(count(df, level = as.factor(Q19), name = "pre"), count(df, level = as.factor(Q19B), name = "post")) |> mutate(across(pre:post, ~replace_na(., 0)))

#6. Knowledge Q6

left_join(count(df, level = as.factor(Q20), name = "pre"), count(df, level = as.factor(Q20B), name = "post")) |> mutate(across(pre:post, ~replace_na(., 0)))

```

```{r podcast}
#Q7
by_Q42 = df %>% group_by(Q42) %>% summarise(count = n())
by_Q42
```

# Data Analysis


```{r prop-test}
#question 1
prop.test(x = c(51,39), n = c(118, 47), alternative = "less")

#question 2
prop.test(x = c(9, 29), n = c(110, 47), alternative = "less")

#question 3
prop.test(x = c(47, 40), n = c(117, 47), alternative = "less")

#question 4
prop.test(x = c(57, 35), n = c(116, 47), alternative = "less")

#question 5
prop.test(x = c(22, 31), n = c(116, 46), alternative = "less")

#question 6
prop.test(x = c(44, 38), n = c(116, 46), alternative = "less")

#all test are significant
```


### Counts for questions


```{r survey-counts}

#get counts and make tables for publication
#7.

countQ7 = left_join(count(df, level = as.factor(Q21), name = "Pre Count"), count(df, level = as.factor(Q21B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

#8

countQ8 = left_join(count(df, level = as.factor(Q22), name = "Pre Count"), count(df, level = as.factor(Q22B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

# 9. 

countQ9 = left_join(count(df, level = as.factor(Q23), name = "Pre Count"), count(df, level = as.factor(Q23B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

# 10. 


countQ10 = left_join(count(df, level = as.factor(Q24), name = "Pre Count"), count(df, level = as.factor(Q24B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

# 11.	

countQ11 = left_join(count(df, level = as.factor(Q38), name = "Pre Count"), count(df, level = as.factor(Q38B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

# 12.	

countQ12 = left_join(count(df, level = as.factor(Q39), name = "Pre Count"), count(df, level = as.factor(Q39B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

#13.	

countQ13 = left_join(count(df, level = as.factor(Q40), name = "Pre Count"), count(df, level = as.factor(Q40B), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

# 14. 

countQ14 = left_join(count(df, level = as.factor(Q25), name = "Pre Count"), count(df, level = as.factor(Q34), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))

#  15. 

countQ15 = left_join(count(df, level = as.factor(Q26), name = "Pre Count"), count(df, level = as.factor(Q37), name = "Post Count")) |> mutate(across(`Pre Count`:`Post Count`, ~replace_na(., 0)))


#ggtexttable(countQ7, rows = NULL, theme = ttheme("mBlueWhite")) %>%  tab_add_title(text ="ABC")
testlist = list(countQ7, countQ8, countQ9, countQ10, countQ11, countQ12, countQ13, countQ14, countQ15)
listoftabs = map(testlist, ggtexttable, rows = NULL, theme = ttheme("mBlueWhite"))

titleQ7 = paste0("string",
                 " string:") %>% strwrap(width = 35) %>% paste(collapse = "\n")
titleQ8 = paste0("string", 
                 "string", "string") %>% strwrap(width = 35) %>% paste(collapse = "\n")


#listoftitles = list(titleQ7, titleQ8, titleQ9, titleQ10, titleQ11, titleQ12, titleQ13, titleQ14, titleQ15)
listoftabs[[1]] %>% tab_add_title(text = titleQ7, size = 10)
listoftabs[[2]] %>% tab_add_title(text = titleQ8, size = 10)
listoftabs[[3]] %>% tab_add_title(text = titleQ9,  size = 10)
listoftabs[[4]] %>% tab_add_title(text = titleQ10, size = 10)
listoftabs[[5]] %>% tab_add_title(text = titleQ11, size = 10)
listoftabs[[6]] %>% tab_add_title(text = titleQ12, size = 10)
listoftabs[[7]] %>% tab_add_title(text = titleQ13, size = 10)
listoftabs[[8]] %>% tab_add_title(text = titleQ14, size = 10)
listoftabs[[9]] %>% tab_add_title(text = titleQ15, size = 10)
```



### Plots

```{r barplots}
#melt(as.data.frame(countQ14) because R and dplyr do not play nice with melt, need to explicitly convert to df
#plots require heavy customization. For publication
plot_q7 = ggplot(melt(as.data.frame(countQ7)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q1") + theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q8 = ggplot(melt(as.data.frame(countQ8)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) + 
            labs(x = "Score", y = 'Count',
                 title = "Q2") + theme_minimal() + 
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q9 = ggplot(melt(as.data.frame(countQ9)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q3") + theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q10 = ggplot(melt(as.data.frame(countQ10)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q4") + theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q11 = ggplot(melt(as.data.frame(countQ11)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q5") + theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q12 = ggplot(melt(as.data.frame(countQ12)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q6") + theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q13 = ggplot(melt(as.data.frame(countQ13)) , aes(x = `level`, y = `value`, fill = `variable`)) +
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q7") + 
  theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q14 = ggplot(melt(as.data.frame(countQ14)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Selected Answer", y = 'Count',
                 title = "Q8") + theme_minimal()+
  theme(axis.title = element_text(size = 9), plot.title = element_text(size = 7, face = "bold"))

plot_q15 = ggplot(melt(as.data.frame(countQ15)) , aes(x = `level`, y = `value`, fill = `variable`)) + 
  geom_bar(stat="identity", width=.5, position = "dodge", alpha = .9) +
            labs(x = "Score", y = 'Count',
                 title = "Q9") + 
  theme_minimal()+ theme(axis.title = element_text(size = 9), plot.title = element_text(size = 9, face = "bold"))
#More plot customization
plot_q7 = plot_q7 + labs(tag = "A") + geom_text(stat = "identity", aes(label = `value`), vjust = -.2, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom", legend.title = element_blank())

plot_q8 = plot_q8 + labs(tag = "B") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom", legend.title = element_blank())

plot_q9 = plot_q9 + labs(tag = "C") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom", legend.title = element_blank())

plot_q10 = plot_q10 + labs(tag = "D") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom", legend.title = element_blank())

plot_q11  = plot_q11 + labs(tag = "E") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
                                      theme(legend.position = "bottom", legend.title = element_blank())

plot_q12 = plot_q12 + labs(tag = "F") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom", legend.title = element_blank())

plot_q13 = plot_q13 + labs(tag = "G") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom",legend.title = element_blank())

plot_q14 = plot_q14 + labs(tag = "I") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "bottom", legend.title = element_blank())

plot_q15 = plot_q15 + labs(tag = "H") + geom_text(stat = "identity", aes(label = `value`), vjust = -.5, 
                                      position = position_dodge(width =.5), size = 2) + 
  theme(legend.position = "right",legend.title = element_blank())


p1 = ggarrange(plot_q7, plot_q8,plot_q9, plot_q10, plot_q11, plot_q12,
               plot_q13, plot_q15, plot_q14, common.legend = TRUE, legend = "bottom",
               nrow = 2, ncol = 2)

multi.page = ggarrange(plot_q7, plot_q8, plot_q9, plot_q10, plot_q11,
                       plot_q12, plot_q13, plot_q14, plot_q15, nrow = 2, ncol = 2,
                       common.legend = T, legend = "bottom")
multi.page[[1]] # Visualize page 1
multi.page[[2]] # visualize page 4
multi.page[[3]] #Visualize page 3

```

# Statsitcal Testing

### Survey quesiton 7, pre q21, post q21B


```{r analysis-q7}
mean(as.numeric(df$Q21), na.rm = T)
mean(as.numeric(df$Q21B), na.rm = T)
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()
# survey question 7, pre q21, post q21b

x=df$Q21
  y=df$Q21B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]
  
#X = c(xp, xu)
#Y = c(yp, yu)
#mean(as.numeric(df$Q21), na.rm = T)
#mean(as.numeric(df$Q21B), na.rm = T)
#mean(X)
#mean(Y)
#cbind(as.numeric(df$Q21), as.numeric(df$Q21B))
rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, mu = 0, alternative = "less", method = "EH")


```



### Survey quesiton 8, pre q22, post q22B
```{r analysis-q8}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()

# Survey quesiton 8, pre q22, post q22B
x=df$Q22
  y=df$Q22B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]

rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")


```




### Survey quesiton 9, pre q23, post q23B

```{r analysis-q9}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()

# Survey quesiton 9, pre q23, post q23B

x=df$Q23
  y=df$Q23B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]
X = c(xp, xu)
Y = c(yp, yu)
rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")

```


### Survey question 10, pre q24, post q24B

```{r analysis-q10}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()
# Survey question 10, pre q24, post q24B

x=df$Q24
  y=df$Q24B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]

rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")

```

### Survey question 11, pre 38, post q38B

```{r analysis-q11}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()
# Survey question 11, pre 38, post q38B

x=df$Q38
  y=df$Q38B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]

rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")


```



 
### Survey question 12, pre 39, post q39B

```{r analysis-q12}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()
# Survey question 12, pre 39, post q39B

x=df$Q39
  y=df$Q39B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]

rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")

```



### Survey question 13, pre 40, post q40B

```{r analysis-q13}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()
# Survey question 13, pre 40, post q40B

x=df$Q40
  y=df$Q40B
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
yu=mean(yp) 
#yu=filter(all,is.na(x) & !is.na(y))[,2]
X = c(xp, xu)
Y = c(yp, yu)
mean(X)
mean(Y)
rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")
?rankb

```




### Survey Question 15, pre 26, post q37

```{r analysis-q15}
#reinitiate empty vectors
xp = numeric()
yp = numeric()
xu = numeric()
yu = numeric()
# Survey question 15, pre 26, post q37

x=df$Q26
  y=df$Q37
 all=data.frame(x,y)
 complete=na.omit(all)
 
 xp=complete[,1]
 yp=complete[,2]
 
 xu=filter(all,!is.na(x) & is.na(y))[,1]
 yu = filter(all,is.na(x) & !is.na(y))[,2] 


 mean(xp)
 mean(yp)
 mean(xu)
rankb(xp, yp, xu, yu, alternative = "less")
permb(xp, yp, xu, yu, alternative = "less",mu = 0, method = "EH")

#cbind(as.numeric(df$Q26), as.numeric(df$Q37))

```







